---
title: "Chapter 3 Homework"
author: "1678226 Chanmi  Yoo (유찬미)"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Regression Analysis  
20657-02  
Jae Keun Yoo  
Oct 14, 2019  


### Q3.4  
### (a)

The dot plot for the number of copiers serviced $X_i$ is:

```{r}
data0304 <- read.table("../Data Sets/Chapter  3 Data Sets/CH03PR04.txt"); names(data0304) <- c("Y", "X", "X2", "X3")
lm.0304 <- lm(Y~X, data=data0304)

dotchart(data0304$X)
```

This plot shows that they are evenly distributed and there is no outlier.
  
### (b)

The time plot for the number of copiers serviced is:

```{r}
plot(seq(nrow(data0304)), data0304$Y, 
     xlab = "time", ylab = "the number of copiers serviced")
```
  
There is no special pattern in this time plot. The number of copiers serviced was not correlated over time.
  
### (c)

The stem-and-leaf plot of the residuals is:

```{r}
resd <- lm.0304$resid
stem(resd)
```

The distribution of residuals is slightly skewed to the right.  
  
  
### (d)
  
```{r}
fitted <- lm.0304$fitted

abs.resd <- abs(resd)

sqrt.mse <- summary(lm.0304)[[6]]; std.resd <- resd / sqrt.mse

par(mfrow=c(1,2))  #화면을 1*2로 분할 
plot(fitted, resd,
     xlab="fitted", ylab="residual") 
plot(data0304$X, resd,
     xlab="X", ylab="residual") 
```
  
Yes, two plots provide the same information.  
Since the variance of residuals seems to be constant over different $X$ and $\hat Y$ levels, errors($\varepsilon_i$) have constant variance. The constant variance assumption of simple linear regression was not violated.     

### (e)  
  
```{r}
new_resd <- order(resd)
qq.r <- qqnorm(new_resd); qq.r
qqline(new_resd)

cor(qq.r$x, qq.r$y)

```

The coefficient of correlation between the ordered residuals and their expected values under normality is 0.989. With n=45, the critical value for the coefficient of correlation n between the ordered residuals and the expected values at $\alpha$ = 0.01 is 0.979. Since 0.989 > 0.979, the assumption of normality appears to be tenable.  
  
### (f)  

```{r}
plot(seq(nrow(data0304)), data0304$Y,
     xlab="time", ylab="residual")

```
 
The residual plot against time did not show any evidence that error terms were correlated over time.  

### (g)
  
To check whether if the error variance varies with the level of X, the alternatives would be:  

$$\begin{cases}H_0 \;:\;  \gamma_{1} = 0 \\
H_a \;:\; \gamma_{1} \neq 0
\end{cases}$$ at $\alpha = .05$ 
  
```{r}
ano <- anova(lm.0304)
ssr <- ano$`Sum Sq`[[1]]; ssr
sse <- ano$`Sum Sq`[[2]]; sse 

```
    
Hence the test statistic is:  

$$X^2_{BP} = \frac{SSR^*}{2} \div \Big(\frac{SSE}{n}\Big)^2 = \frac{76960.42^*}{2} \div \Big(\frac{3416.377}{45}\Big)^2 = 6.6762$$
  
The decision rule is:

$$\begin{cases}\text{If } |X^2_{BP}| \leq  \chi^2( .95 \; ; \, 1) \text{, conclude } H_0  \\
\text{If } |X^2_{BP}| >  \chi^2( .95 \; ; \, 1) \text{, reject } H_0 \end{cases}$$
  
$\chi^2( .95 \; ; \, 1)$ is:

```{r}
round(qchisq(.95, 1), 4)
```  
  
Since $X^2_{BP} = 6.6762 > 3.8415$, reject $H_0$(conclude $H_a$). Thus, the error variance is not constant.  

### (h)

```{r}
par(mfrow=c(1,2)) 
plot(data0304$X2, resd,
     xlab="X2", ylab="residual")
plot(data0304$X3, resd,
     xlab="X3", ylab="residual")
``` 

The residual versus $X_2$ plot showed a positive linear trend. It means that the regression model might be improved by including $X_2$.  
The residual versus $X_3$ plot did not show any special pattern. So, adding $X_3$ into the model may not bring any improvement in terms of model fitting.  
  
  
### Q3.6  
### (a)

The dot plot for the number of copiers serviced $X_i$ is:

```{r}
data0306 <- read.table("../Data Sets/Chapter  1 Data Sets/CH01PR22.txt"); names(data0306) <- c("Y", "X")
lm.0306 <- lm(Y~X, data=data0306)
resd <- lm.0306$residuals; resd
boxplot(resd, main = "Boxplot of the residuals")
```

The distribution of residuals is symmetric with the mean of 0.  

### (b)
  
```{r}
fitted <- lm.0306$fitted.values
plot(fitted, resd)
```
  
There is no special pattern in the residual versus fitted plot. The range of fitted values is (200, 250) and residuals are evenly distributed. Thus, the error variance is constant.  
  
### (c)
  
```{r}
qq.r <- qqnorm(resd); qq.r
qqline(resd)
cor(qq.r$x, qq.r$y)
plot(fitted, resd)
```

### (d)

```{r}
qt(0.25,15); qt(0.5,15); qt(0.75,15); qt(1,15)

```

### (e)

To check whether if the error variance varies with the level of X, the alternatives would be:  

$$\begin{cases}H_0 \;:\;  d_{i1} - d_{i2} = 0 \text{ (The variance of residuals from two groups are equal)} \\
H_a \;:\;  d_{i1} - d_{i2} \neq 0 \text{ (The variance of residuals from two groups are not equal)}
\end{cases}$$ at $\alpha = .05$ 

The medians of the residuals in the two groups are:
  
```{r}
nrow(data0306)  # Since the number of observed vaules is 16, divide the groups in to size of 8 each.
resd1 <- resd[1:8]
resd2 <- resd[9:16]
d1 <- sum(abs(resd1-median(resd1)))
d2 <- sum(abs(resd2-median(resd2)))
d1 - d2
s <- sqrt((sum((resd1-median(resd1))^2) + sum((resd2-median(resd2))^2) ) / nrow(data0306) - 2); s
```
    
Hence the test statistic is:  

$$t^*_{BF} = \frac{\bar{d_1} - \bar{d_2}}{s \sqrt{\frac{1}{n_1} + \frac{1}{n_2}}} = \frac{5.9}{2.7022 * \sqrt{\frac{1}{8} + \frac{1}{8}}} = 4.3668$$
  
The decision rule is:

$$\begin{cases}\text{If } |t^*_{BP}| \leq  t( .95 \; ; \, 14) \text{, conclude } H_0  \\
\text{If } |t^*_{BP}| >  t( .95 \; ; \, 14) \text{, reject } H_0 \end{cases}$$
  
$\chi^2( .95 \; ; \, 1)$ is:

```{r}
round(qt(.95, 14), 4)
```  
  
Since $t^*_{BP} = 2.7022 > 1.7613$, reject $H_0$(conclude $H_a$). Thus, the error variance is not constant.  


